### 2011-01-07 proof.pre.tex
Delegate formatting details to TeX commands

\documentclass{article}
\usepackage{holtexbasic}
\usepackage{alltt}
\usepackage[a4paper,margin=2cm]{geometry}
\usepackage{parskip}
\begin{document}
\section*{Introduction}
Update: Contrary to my earlier warning when I write \HOLtm{SIGMA (\m. f m) (count (SUC b))} I now mean for the variable $m$ to range from $0$ up to \emph{and including} $b$, as per the usual convention.

This file contains the statements of a few key lemmas, as well as proof sketches for the important lemmas.
How to read the proofs?
Imagine you are trying to prove the statement yourself.
There are snapshots of the ``proof state'' interspersed with commentary on what to do next to get to the next proof state.
A proof state consists of what is currently remaining to be proved, then a line of dashes (\texttt{----------}) then a numbered list of assumptions that are currently being assumed.
(Note: sometimes we might be proving a subsidiary goal, and the proof state of the whole goal isn't printed until that subgoal is finished; I try to make this clear with the commentary.)

>>>>

\documentclass{article}
\usepackage{holtexbasic}
\usepackage{alltt}
\newcommand{\HOLAsmSep}{\texttt{----------}}
\usepackage[a4paper,margin=2cm]{geometry}
\usepackage{parskip}
\begin{document}
\section*{Introduction}
Update: Contrary to my earlier warning when I write \HOLtm{SIGMA (\m. f m) (count (SUC b))} I now mean for the variable $m$ to range from $0$ up to \emph{and including} $b$, as per the usual convention.

This file contains the statements of a few key lemmas, as well as proof sketches for the important lemmas.
How to read the proofs?
Imagine you are trying to prove the statement yourself.
There are snapshots of the ``proof state'' interspersed with commentary on what to do next to get to the next proof state.
A proof state consists of what is currently remaining to be proved, then a line of dashes (\HOLAsmSep{}) then a numbered list of assumptions that are currently being assumed.
(Note: sometimes we might be proving a subsidiary goal, and the proof state of the whole goal isn't printed until that subgoal is finished; I try to make this clear with the commentary.)
